Estimating duration in the presence of misclassification

### 2024-03-29 introduction_new.tex

The overall question that I investigate in this thesis is whether a prevalence survey \emph{alone} is sufficient to infer incidence and transmission and, if so, what method(s) are optimal?
% First, how can prevalence surveys be designed to help estimate these quantities?

>>>>

The overall question that I investigate in this thesis is: can a prevalence survey \emph{alone} be sufficient to infer incidence and transmission and, if so, what method(s) are optimal?
% First, how can prevalence surveys be designed to help estimate these quantities?
